---
title: "Challenge B"
author: "Cosma, Bianca & García Bouyssou, Clara"
date: "December 2nd 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE, include=FALSE}
#install packages:
install.packages("tidyverse")
install.packages("gridExtra")
install.packages("caret")
install.packages("stringi")
install.packages("np")
install.packages("random.Forest")
install.packages("dplyr")
install.packages("readr")
```

```{r, include=FALSE}
#require packages:
require(tidyverse)
require(gridExtra)
require(caret)
require(stringi)
require(np)
require(randomForest)
require(dplyr)
require(readr)
require(data.table)
```

#Task 1B - Predicting house prices in Ames, Iowa (continued)

```{r, include=FALSE}
#We upload the datasets
train<-read.csv(file="C:/Users/clara/rprog/Challenge B/train.csv",header=T,dec=",")
test<-read.csv(file="C:/Users/clara/rprog/Challenge B/test.csv",header=T,dec=",")
linearpredictions<-read.csv(file="C:/Users/clara/rprog/Challenge B/predictionBiancaClara.csv",header=T,dec=",")

#Then we store the Id as a variable
linear<-data.frame(linearpredictions)
Id <- rownames(linear)
linear <- cbind(Id=Id, linear)

```
##Step 1 
Random forest algorithms are used for regression and classification models. Compare to other models it relies on fewer assumptions. The prediction is made on 2/3 of the training sample. This subsample is created by random selection of  cases(observations) with replacement and it is used to grown the trees. Then a subsample of inputs (independent variables) are selected at random. Afterwards the remaining part of the sample it is used to calculate the Out-Of-the-Bag (OOB) error rate. Each tree gives a classifation on the OOB, then the classification having the most votes is choosen. In the case is tackled here, a regression model, the classification is the average of the outcome(dependent variable).

##Step 2
A model is created with random forest and the results are presented below:
```{r, include=FALSE}
#We create a vector called SalePrice, with the same dimensions of a column of the test dataset

SalePrice<-c(1:1459)

#This new column is bounded with the dataset
testcomp<-cbind(test, SalePrice)

#So we can finally bind the rows of train and test
total<-rbind(train, testcomp)

#We apply the norm we applied in the last challenge to get rid of the variables with too many NA's, none variable with more than a 10% of NA's will remain in the dataset "total.improved"
total.improved<-total[, -which(colMeans(is.na(total)) > 0.1)]


#We then split again the test and the train, by the Id, and we eliminate the variable Id for both, and the SalePrice previously created in test2
train1<-filter(total.improved, Id<1461)
train2<-train1[ , -which(names(train1) %in% c("Id"))]

test1<-filter(total.improved, Id>1460)
test2<-test1[ , -which(names(test1) %in% c("SalePrice", "Id"))]


```
```{r, include=FALSE}
#We estimate the random forest model and we get the tree
model1<-randomForest(SalePrice~., data=train2, na.action=na.exclude)
getTree(model1, 1)
```
 
```{r, echo=FALSE, comment=NA} 
#Here it is the summary of our model
 summary(model1)
``` 
##Step 3

Once the predictions using random forest model are computed, they are plotted together with the predictions from the linear model obtained in Challenge A. It is possible to observe a diference between the two predictions. Moreover, in the linear model we obtained an important outlier that does not appear in this machine learning technique.

```{r, include=FALSE}
#We make predictions using the model1:
prediction<-predict(model1, test2, type="response", norm.votes = TRUE)

#we bind the predictions with with the Id
prediction1<-cbind(test1$Id, prediction)

#The column names of the dataset of both predicitons are changed:
colnames(prediction1)<-c("Id","prediction")
colnames(linear)<-c("Id","linpred")

#Therefore we can proceed to merge both datasets by Id:
prediction2<-merge(linear, prediction1, by="Id")

#In order to use ggplot2 we need all the variables to be numeric so we run the following loop:
prediction2[] <- lapply(prediction2, function(x) {
    if(is.factor(x)) as.numeric(as.character(x)) else x})
sapply(prediction2, class)
```

```{r, echo=FALSE, comment=NA}
#Here is the graph of the comparition between the predictions we made with the linear model in Challenge A and the prediction we made with rainForest
graph<-ggplot(prediction2, aes(x = Id)) + 
  geom_line(aes(y = prediction), colour="blue", show.legend = TRUE) + 
  geom_line(aes(y = linpred), colour = "red", show.legend = TRUE, linetype="dotted") + 
  ylab(label="Prediction of SalePrice") + 
  xlab("Id")+ 
  ggtitle("Linear vs Random Forest Predicted Price")
graph
```





#Task 2B - Overfitting in Machine Learning (continued)

```{r, include=FALSE }

#we create two datasets from the prvious challenge, storing the values for the training and test samples of the variables y and x
training_ML<-read.csv(file="C:/Users/clara/rprog/Challenge B/training_ML.csv",header=T,dec=",")
test_ML<-read.csv(file="C:/Users/clara/rprog/Challenge B/test_ML.csv",header=T,dec=",")

#we convert the variables from factors to numeric for training
training_ML[] <- lapply(training_ML, function(x) {
    if(is.factor(x)) as.numeric(as.character(x)) else x})
sapply(training_ML, class)

#we convert the variables from factors to numeric for test
test_ML[] <- lapply(test_ML, function(x) {
    if(is.factor(x)) as.numeric(as.character(x)) else x})
sapply(test_ML, class)

#we save the colums of y and x from training as vectors
y<-training_ML[,1]
x<-training_ML[,2]

#we save the colums of y and x from test as vectors
yt<-test_ML[,1]
xt<-test_ML[,2]

```
##Step 1
By employing the training dataset a low flexibility local linear model is constructed. Summary is displayed below:
```{r, echo=FALSE, comment=NA}

#we estimate a low-flexibility local linear model on the training data
ll.fit.lowflex<-npreg(y~x, bws=0.5, data=training_ML,regtype="ll")
summary(ll.fit.lowflex)
```

## Step 2
With the same procedure a high flexibility local linear model is created using the training dataset:
```{r, echo=FALSE, comment=NA}

#we estimate a low-flexibility local linear model on the test data
ll.fit.highflex<-npreg(y~x, bws=0.01, data=training_ML,regtype="ll")
summary(ll.fit.highflex)
```

##Step 3
The following scatterplot reports the values of x and y and the prediction of the low (blue) and high (red) flexibility models in the training dataset.
```{r, include=FALSE}

#we compute the predictions of the low and high flexibility models on the training data
fit_low<-predict(ll.fit.lowflex,data=training_ML)
fit_high<-predict(ll.fit.highflex,data=training_ML)
```

```{r, echo=FALSE, comment=NA}

#we create a graph with the variables y and x from the training data, we plot the predictions from the low and high flexibility models
graph1<-ggplot() +
  geom_point(aes(training_ML$x, training_ML$y)) +
  geom_line(aes(training_ML$x, fit_low), color="blue", size=1) +
  geom_line(aes(training_ML$x, fit_high), color="red", size=1)+
  xlab("X - training")+
  ylab("Y - training")
graph1
```

##Step 4
It is possible to observe that the high flexibility model leads to more variance in the predictions. On the other hand, the low flexibility model increases the bias i.e. the distance between the prediction and the value. Therefore, is necesssary to find the right balance between overfitting and underfitting respectively.

##Step 5
The following scatterplot presents the values of y and x along with the predictions of the high and low flexibility models in the test dataset.
```{r, include=FALSE}
#we compute the predictions of the low and high flexibility models on the test data
fit_low_test<-predict(ll.fit.lowflex,newdata=test_ML)
fit_high_test<-predict(ll.fit.highflex,newdata=test_ML)
```

```{r, echo=FALSE, comment=NA}

graph2<-ggplot() +
  geom_point(aes(test_ML$x, test_ML$y)) +
  geom_line(aes(test_ML$x, fit_low_test), color="blue", size=1) +
  geom_line(aes(test_ML$x, fit_high_test), color="red", size=1)+
  xlab("X - test")+
  ylab("Y - test")
graph2
```

The high flexibility model has still the highest variance among predictions. Besides, being this the least biased model it can be seen that the fitted model does not addapt properly to the new sample. In fact, the original variance of the model does not reflect the variance of the new sample.


##Step 6
First of all, a vector with different bandwidths is created in order to construct models with different degrees of flexibility.
```{r, include=FALSE}
#we create a vector of different bandwidths
bandwidth <- seq(0.01, 0.5, by = 0.001)

```

##Step 7
A function was employed to creat a model for each value in the bandwidth interval in the training dataset.
```{r,include=FALSE}
#We create a model for each bandwith

llbw.fit <- lapply(X = bandwidth, FUN = function(bandwidth) {npreg(y ~ x, bws = bandwidth, data = training_ML, method = "ll")})
```

##Step 8
After computing the predictions in the training dataset for each model the mean squared error is computed.
```{r, echo=FALSE, comment=NA}
#First we compute the predicitions for all the models on the training dataset

fit_all <- predict(llbw.fit, newdata=training_ML)
fitall<-data.frame(fit_all)
colnames(fitall)<-c(1:length(fitall))

#We compute the MSE for each model

MSE<- apply(fitall, 2, function(a){mean((a-y)^2)})
summary(MSE)
```

##Step 9
The previous step is repeated on the test dataset.
```{r, include=FALSE}
#We repeat the procedure for the test dataset

fit_all1 <- predict(llbw.fit, newdata=test_ML)
fitall1<-data.frame(fit_all1)
colnames(fitall1)<-c(1:length(fitall1))

MSE1<- apply(fitall1, 2, function(a){mean((a-yt)^2)})

```


#Step 10
The following graph summarises how de MSE changes with respect to the bandwidth in the two samples i.e. blue for the training dataset and red for the test.
It can be concluded that the MSE in the test dataset reaches a minimum for intermediate values of the bandwidht i.e. 0.2, instead in the training dataset the mean squared error is almost proportionally increasing with the bandwidth. Therefore it is preferable to use a value around the median of the bandwidth.
```{r, echo=FALSE, comment=NA}
#We plot the MSE for each model depending on the bandwidth with respect to the training and test samples

graph3<-ggplot() +
  geom_line(aes(bandwidth, MSE), color="blue", size=1) +
  geom_line(aes(bandwidth, MSE1), color="red", size=1)+
  xlab("Bandwidth")+
  ylab("MSE")
graph3
```

#Task 3B - Privacy regulation compliance in France

##Step 1
For the next steps the dataset CNIL will be employed.
```{r, include=FALSE}
CNIL <- read_delim("C:/Users/clara/rprog/Challenge B/CNIL.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
```

##Step 2
The following table sumarizes how many organizations in France have adhered to the CNIL per department i.e. they have a CIL.
```{r, echo=FALSE, comment=NA}
#First we extract the department from the two first digits of the Code Postal
department <- substr(CNIL$Code_Postal, 0, 2)

#We create a vector of ones of the length of a column

one<-c(1:length(CNIL$Siren))

#We bind the pre-loaded dataset with the new columns

cnil<-cbind(CNIL, department, one)

#We sum the vector of ones by department
count1<-aggregate(cnil$one, by=list(Category=cnil$department), FUN=sum)

#We drop unclear data for the departments
count2<-count1[- c(1, 99:108),]

#We name our columns
colnames(count2)<-c("Department","Number of organizations with CIL")

#We create a table
count3<-setDT(count2)
count3
```


##Step 3
First of all the dataset SIRC was imported. Then, it was merge whith the dataset cnil by the variable SIREN.
```{r, include=FALSE}
#We eliminate the vector of ones we used to count
cnil1<-cnil[ , -which(names(cnil) %in% c("one"))]

#We change the names of the variables to match SIREN
colnames(cnil1)<-c("SIREN","Responsable", "Adresse", "Code_Postal", "Vile", "NAF", "TypeCIL", "Portee", "department")

#We use this function to optimaze the reading of the huge dataset
SIRC <- fread("C:/Users/clara/rprog/Challenge B/SIRC.csv")

#In order to work with a vector of the more than 80Mb we used the following comand:
memory.limit(10000000)

#Then we merge cnil1 and SIRC by SIREN
cnil2<-merge(cnil1,SIRC, by="SIREN")
```

##Step 4
The dataset presents information on the employment size of the various companies. This variable is categorical with the numeric values that represent the size. In the histogram it is seen that companies that have employment size greater than 2000 employees (categories greater than 51 \footnote{https://www.sirene.fr/sirene/public/variable/tefen}) have the highes frequency.
```{r, echo=FALSE, comment=NA }
#We convert the variable from character to numeric
TEFEN2<-as.numeric(cnil2$TEFEN)

#We plot the histogram
graph4<-hist(TEFEN2)
graph4
```

